The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
forage > lichen

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (open, forest and lichen) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

@@

<!-- Figure 3: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, forage, and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g. open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for lichen layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, forage, and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter lichen layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that lichen layer similarity is not shown because
individuals did not interact in lichen habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, forage, and open) across two seasons (summer and
winter) and four network metrics calculated. A) Mean graph strength across
individuals varied for winter layers becoming relatively stable at 200
observations and remained weak throughout for summer layers. B) Mean layer
relevance across individuals increased for winter layers and slightly increased
for summer layers. C) Similarity of landcover network layers between seasons
(e.g. open summer compared to open winter) showed a stabilizing layer similarity
at 200 observations for forest and 300 observations for lichen and open. D) Mean
connective redundancy across individuals increased with increasing number of
observations, which begins to plateau around 100 observations. Note, data in
panel C are truncated because there were few observations of individuals in
foraging and open habitats during the winter, resulting in inability to
calculate layer similarity at lower number of observations.

@@

(ref:winlen) Varying scale in time window length. For each time window length
(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
were constructed for each landcover class (forest, lichen and open) across two
seasons (summer and winter) and four network metrics calculated. A) Mean graph
strength across individuals was relatively stable over increasing time window
lengths, though there was more variation in strength between landcover types as
window length increased. <!--TODO:**[see if you agree with my changes. B-D were
based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
generally increased during the summer months but was relatively stable across
time window lengths for each landcover layer. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
increasing similarity consistent across landcover layers with increasing window
length. D) Mean connective redundancy across individuals varied dramatically
depending on the length of the time window <!--TODO:**[JWT: previously this was
describing fig. 3. I don't know if what I wrote best encapsulates what
connnective redundancy does here. Length of time window seems to make connective
redundancy highly variable as it changes.]**.-->

@@

(ref:winpos) Varying scale in time window position. For each time window
position (shifting the start date of the time window used to define seasons 1 to
48 days from the original), multilayer networks were constructed for each
landcover class (forest, lichen and ope) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
increased in summer network layers at window position 25 and increased between
window position 20 and 40 for winter network layers. B) Mean layer relevance
slightly decreased for winter layers and increased for summer layers, showing
decreasing connectivity in shifted winter time windows and greater connectivity
in summer layers at later window positions. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
fluctuations in layer similarity across landcover types with shifted time
windows. <!--TODO:**[JWT: previously describing window length, not position.
Check that you're ok with my changes]**--> D) Mean connective redundancy across
individuals increased between window position 12 through 48 due to increased
connectivity in the summer network layers.

>>>>

We generated a multilayer social network consisting 16 individual nodes and two
aspects (season and landcover). Two season elementary-layers (winter and summer)
and three landcover elementary-layers (forest, forage, and open) combined for a
total of six layers. Layers were composed of individuals represented as nodes
and social associations represented as edges, for each season and landcover
combination. Proximity-based social network layers were generated using the R
package `spatsoc` [@Robitaille_2019] in `r version$version.string`
[@R_Core_Team_2019]. <!-- TODO: FIX VANDER WAL IN SPATSOC REF -->

@@

<!-- Figure 3: metrics by social scale -->
(ref:socres) Varying scale in social threshold. For each social threshold, multilayer
networks were constructed for each landcover class (forest, forage, and open)
across two seasons (summer and winter) and four network metrics calculated.  A)
Mean graph strength across individuals showed an increase for winter network
layers at 50 m through 500 m while summer network layers had consistently weak
connections. B) Mean layer relevance was relatively stable across social
thresholds for each season and landcover layer. C) Similarity of landcover
network layers between seasons (e.g. open summer compared to open winter)
showed different responses to changing landcover scale with an overall increase
in similarity for open layers and decrease in similarity for forage layers.
<!--TODO: what about forest.--> D) Mean connective redundancy across individuals
increased rapidly between 5 m and 50 m reaching a plateau  of about 0.65 at
approximately a 50 m <!--TODO:**??**--> social threshold before decreasing
between 400 m and 500 m.

@@

<!-- Figure 4: metrics by landcover resolution -->
(ref:lcres) Variation in multilayer network metrics as a function of changes in
landcover resolution, a metric which we interpret as spatial scale. For each
landcover resolution, multilayer networks were constructed for each landcover
class (forest, forage, and open) across two seasons (summer and winter), and four
network metrics were calculated and we examined how network metrics changed as a
function of changes in spatial scale. A) Mean graph strength of individuals was
weaker during the summer compared to the winter months. B) Mean layer relevance
showed sparse connectivity in summer compared to winter networks and a decrease
in winter forage layer relevance at higher landcover resolutions. C) Similarity
of landcover network layers between seasons (e.g. open summer compared to open
winter) showed different responses to changing landcover scale with an increase
in similarity for forest layers at 250 m and decrease in similarity for open
layers at 250 m. Note that forage layer similarity is not shown because
individuals did not interact in forage habitats greater greater than 10 m
landcover resolution. D) Mean connective redundancy across individuals showed a
decreasing trend with increasing landcover resolution.

@@

<!-- Figure 5: metrics by number of observations -->
<!-- TODO: RO first sentence... -->
(ref:nobs) Varying scale in number of observations. For each iteration, a number
of observations (10-485 observations in steps of 25) were selected from the
complete data set to construct multilayer networks with layers defined by each
landcover class (forest, forage, and open) across two seasons (summer and
winter) and four network metrics calculated. A) Mean graph strength across
individuals varied for winter layers becoming relatively stable at 200
observations and remained weak throughout for summer layers. B) Mean layer
relevance across individuals increased for winter layers and slightly increased
for summer layers. C) Similarity of landcover network layers between seasons
(e.g. open summer compared to open winter) showed a stabilizing layer similarity
at 200 observations for forest and 300 observations for forage and open habitats. D) Mean
connective redundancy across individuals increased with increasing number of
observations, which begins to plateau around 100 observations. Note, data in
panel C are truncated because there were few observations of individuals in
foraging and open habitats during the winter, resulting in inability to
calculate layer similarity at lower number of observations.

@@

(ref:winlen) Varying scale in time window length. For each time window length
(40 to 100 days in length increasing by 5 days in sequence), multilayer networks
were constructed for each landcover class (forest, forage, and open) across two
seasons (summer and winter) and four network metrics calculated. A) Mean graph
strength across individuals was relatively stable over increasing time window
lengths, though there was more variation in strength between landcover types as
window length increased. <!--TODO:**[see if you agree with my changes. B-D were
based off fig. 3 and not relevant to this figure]**-->  B) Mean layer relevance
generally increased during the summer months but was relatively stable across
time window lengths for each landcover layer. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
increasing similarity consistent across landcover layers with increasing window
length. D) Mean connective redundancy across individuals varied dramatically
depending on the length of the time window <!--TODO:**[JWT: previously this was
describing fig. 3. I don't know if what I wrote best encapsulates what
connnective redundancy does here. Length of time window seems to make connective
redundancy highly variable as it changes.]**.-->

@@

(ref:winpos) Varying scale in time window position. For each time window
position (shifting the start date of the time window used to define seasons 1 to
48 days from the original), multilayer networks were constructed for each
landcover class (forest, forage, and open) across two seasons (summer and winter)
and four network metrics calculated. A) Mean graph strength across individuals
increased in summer network layers at window position 25 and increased between
window position 20 and 40 for winter network layers. B) Mean layer relevance
slightly decreased for winter layers and increased for summer layers, showing
decreasing connectivity in shifted winter time windows and greater connectivity
in summer layers at later window positions. C) Similarity of landcover network
layers between seasons (e.g. open summer compared to open winter) showed
fluctuations in layer similarity across landcover types with shifted time
windows. <!--TODO:**[JWT: previously describing window length, not position.
Check that you're ok with my changes]**--> D) Mean connective redundancy across
individuals increased between window position 12 through 48 due to increased
connectivity in the summer network layers.
